---
title: "PondGraphics"
author: "Dylan Titmuss"
date: "2023-12-26"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Load packages
```{r setup, include = FALSE}
library(tidyverse)
library(egg)
```

## Load data
```{r}
# load surface-only data
allSurface <- read.csv("data/AllPonds_Surface.csv") %>%
  mutate(across(where(is.character), ~ na_if(., "#N/A"))) %>%
  mutate(DepthClass = factor(DepthClass, levels = c("Shallow", "Deep"))) %>%
  mutate(DevelopmentClass = factor(DevelopmentClass, levels = c("Very Low", "Low", "Medium", "High", "Very High"))) %>%
  mutate(SurfaceAreaClass = factor(SurfaceAreaClass, levels = c("Very Small", "Small", "Medium", "Large")))

## define "consistently sampled" ##

subSurface_pre <- allSurface %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2003 & Year <= 2013)   ### inclusive or exclusive of 2003 itself?

subSurface_post <- allSurface %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2014)

# load bottom-only data
allBottom <- read.csv("data/AllPonds_Bottom.csv") %>%
  mutate(across(where(is.character), ~ na_if(., "#N/A"))) %>%
  mutate(DevelopmentClass = factor(DevelopmentClass, levels = c("Very Low", "Low", "Medium", "High", "Very High"))) %>%
  mutate(SurfaceAreaClass = factor(SurfaceAreaClass, levels = c("Very Small", "Small", "Medium", "Large")))

allBottom_pre <- allBottom %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2003 & Year <= 2013)

allBottom_post <- allBottom %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2014)
```

## Pt. 1: Summary of new data and data characteristics 
```{r}
params <- c("TP", "TN", "Chla", "Secchi", "Temp", "DO")

### split time period in half
### put both time periods on same panel (maybe lines instead of filled bars); diff. color for each
### two panels (surface + bottom) per param
### Chla & Secchi on same graphic (both surf panels)

plot_list1 <- lapply(params, function(p) {
  ggplot(allSurface_pre, aes(x = .data[[p]])) + 
    geom_histogram() +
    theme_bw()
})

plot_list2 <- lapply(params[c(1:3, 5:6)], function(p) {
  ggplot(allBottom_pre, aes(x = .data[[p]])) + 
    geom_histogram() +
    theme_bw()
})

plot_list3 <- lapply(params, function(p) {
  ggplot(allSurface_post, aes(x = .data[[p]])) + 
    geom_histogram() +
    theme_bw()
})

plot_list4 <- lapply(params[c(1:3, 5:6)], function(p) {
  ggplot(allBottom_post, aes(x = .data[[p]])) + 
    geom_histogram() +
    theme_bw()
})

ggarrange(ggplot() + annotate(geom = "text", x = 1, y = 1, label = "Surface 2003-2013") + theme_void(),
          ggplot() + annotate(geom = "text", x = 1, y = 1, label = "Bottom 2003-2013") + theme_void(),
          ggplot() + annotate(geom = "text", x = 1, y = 1, label = "Surface 2014-present") + theme_void(),
          ggplot() + annotate(geom = "text", x = 1, y = 1, label = "Bottom 2014-present") + theme_void(),
          plot_list1[[1]],
          plot_list2[[1]],
          plot_list3[[1]],
          plot_list4[[1]],
          plot_list1[[2]],
          plot_list2[[2]],
          plot_list3[[2]],
          plot_list4[[2]],
          plot_list1[[3]],
          plot_list2[[3]],
          plot_list3[[3]],
          plot_list4[[3]],
          plot_list1[[4]],
          ggplot() + theme_void(),
          plot_list3[[4]],
          ggplot() + theme_void(),
          plot_list1[[5]],
          plot_list2[[4]],
          plot_list3[[5]],
          plot_list4[[4]],
          plot_list1[[6]],
          plot_list2[[5]],
          plot_list3[[6]],
          plot_list4[[5]], ncol = 4)
```

### Ecoregion thresholds (Secchi, Chla, TN, TP)
Ponds:
-- Hathaway S (BA)
-- Micah (BA)
-- Slough (BR)
-- Pine (BR)
-- Flax (DE)
-- Slough (TR)
-- Duck (WE)
-- Spectacle (WE)

- Calculate 75%ile using allSurface & using ponds to compare
- Calculate 75%ile threshold values per year using ponds

### DO standard
- Calc "recent" (2016+) & annually in table

### 4a
- All ponds on one graphic; hline @ 3 mg/L
