---
title: "PondGraphics"
author: "Dylan Titmuss"
date: "2023-12-26"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Load packages
```{r setup, include = FALSE}
library(tidyverse)
library(egg)
```

## Load data
```{r}
setwd("~/Desktop/Repos/CapeCodPonds2023")

# load surface-only data
allSurface <- read.csv("data/AllPonds_Surface.csv") %>%
  mutate(across(where(is.character), ~ na_if(., "#N/A"))) %>%
  mutate(DepthClass = factor(DepthClass, levels = c("Shallow", "Deep"))) %>%
  mutate(DevelopmentClass = factor(DevelopmentClass, levels = c("Very Low", "Low", "Medium", "High", "Very High"))) %>%
  mutate(SurfaceAreaClass = factor(SurfaceAreaClass, levels = c("Very Small", "Small", "Medium", "Large")))

## define "consistently sampled" ##

allSurface_pre <- allSurface %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year <= 2011)

allSurface_post <- allSurface %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2012)

# load bottom-only data
allBottom <- read.csv("data/AllPonds_Bottom.csv") %>%
  mutate(across(where(is.character), ~ na_if(., "#N/A"))) %>%
  mutate(DevelopmentClass = factor(DevelopmentClass, levels = c("Very Low", "Low", "Medium", "High", "Very High"))) %>%
  mutate(SurfaceAreaClass = factor(SurfaceAreaClass, levels = c("Very Small", "Small", "Medium", "Large")))

allBottom_pre <- allBottom %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year <= 2011)

allBottom_post <- allBottom %>%
  group_by(Station.name) %>%
  filter(min(Year) <= 2005,
         max(Year) >= 2016) %>%
  filter(n() >= 9) %>%
  ungroup() %>%
  filter(Year >= 2012)
```

### Ecoregion thresholds (Secchi, Chla, TN, TP)
Ponds:
-- Hathaway S (BA)
-- Micah (BA)
-- Slough (BR)
-- Pine (BR)
-- Flax (DE)
-- Slough (TR)
-- Duck (WE)
-- Spectacle (WE)

- Calculate 75%ile using allSurface & using ponds; compare
- Calculate 75%ile threshold values per year using ponds

```{r}
ecoregion <- allSurface %>%
  filter(Station.name == "BA-594-01 / Hathaway Pond (South)" |
         Station.name == "BA-797-01 / Micah Pond" |
         Station.name == "BR-321-01 / Slough Pond" |
         Station.name == "BR-335-01 / Pine Pond" |
         Station.name == "DE-355-01 / Flax Pond" |
         Station.name == "TR-53-01 / Slough Pond" |
         Station.name == "WE-76-01 / Duck Pond" |
         Station.name == "WE-64-01 / Spectacle Pond")

ecoregion2 <- ponds %>%
  filter(Month == 8 | Month == 9) %>%
  filter(Station.name == "BA-594-01 / Hathaway Pond (South)" |
         Station.name == "BA-797-01 / Micah Pond" |
         Station.name == "BR-321-01 / Slough Pond" |
         Station.name == "BR-335-01 / Pine Pond" |
         Station.name == "DE-355-01 / Flax Pond" |
         Station.name == "TR-53-01 / Slough Pond" |
         Station.name == "WE-76-01 / Duck Pond" |
         Station.name == "WE-64-01 / Spectacle Pond")

thresh_Secchi <- quantile(ecoregion$Secchi, na.rm = TRUE)[4]   ### 6.02 vs 6.04
thresh_chla <- quantile(ecoregion$Chla, na.rm = TRUE)[4]   ### 3.06 vs 3.56
thresh_TN <- quantile(ecoregion$TN, na.rm = TRUE)[4]   ### 24.5 vs 23.2
thresh_TP <- quantile(ecoregion$TP, na.rm = TRUE)[4]   ### 0.40 vs 0.45

thresh_Secchi2 <- quantile(ecoregion2$Secchi, na.rm = TRUE)[4]
thresh_chla2 <- quantile(ecoregion2$Chla, na.rm = TRUE)[4]
thresh_TN2 <- quantile(ecoregion2$TN, na.rm = TRUE)[4]
thresh_TP2 <- quantile(ecoregion2$TP, na.rm = TRUE)[4]

eco_annual <- ecoregion2 %>%
  group_by(Year) %>%
  summarise(Secchi = quantile(Secchi, na.rm = TRUE)[4],
            Chla = quantile(Chla, na.rm = TRUE)[4],
            TN = quantile(TN, na.rm = TRUE)[4],
            TP = quantile(TP, na.rm = TRUE)[4])

# quantile(ecoregion2$Secchi[ecoregion2$Year == 2001], na.rm = TRUE)

p1 <- ggplot(eco_annual, aes(x = Year, y = Secchi)) +
  geom_point() +
  geom_hline(yintercept = 4.5, linetype = "dashed") +
  geom_hline(yintercept = 2, linetype = "dashed") +
  ylim(0, 8) +
  theme_bw()

p2 <- ggplot(eco_annual, aes(x = Year, y = Chla)) +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") +
  scale_y_continuous(limits = c(0, 9.5), breaks = c(0, 2, 4, 6, 8)) +
  theme_bw()

p3 <- ggplot(eco_annual, aes(x = Year, y = TN)) +
  geom_point() +
  geom_hline(yintercept = 11.42, linetype = "dashed") +
  ylim(0, 46) +
  theme_bw()

p4 <- ggplot(eco_annual, aes(x = Year, y = TP)) +
  geom_point() +
  geom_hline(yintercept = 0.24, linetype = "dashed") +
  ylim(0, 0.95) +
  theme_bw()

f1 <- ggarrange(p1, p2, p3, p4, ncol = 2)

ggsave("figures/f1.png", f1, width = 6.5, height = 5, units = "in", dpi = 600)
```

## Pt. 1: Summary of new data and data characteristics 
```{r}
### split time period in half
### put both time periods on same panel; lines instead of filled bars; diff. color for each
### two panels (surface + bottom) per param
### Chla & Secchi on same graphic (both surf panels)

colors <- c("2001-2011" = "royalblue", "2012-2023" = "chartreuse3")

Secchi1 <- ggplot(mapping = aes(x = Secchi, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, aes(fill = "2001-2011"), col = NA, alpha = 0.5) +
  geom_histogram(data = allSurface_post, aes(fill = "2012-2023"), col = NA, alpha = 0.5) +
  geom_vline(xintercept = thresh_Secchi2, linetype = "dashed") +
  labs(y = "Proportion", title = "Surface") +
  scale_fill_manual(values = colors) +
  theme_bw() +
  theme(legend.position = c(0.85, 0.8),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6),
        legend.title = element_blank(),
        legend.margin = margin(0, 1, 1, 1, "pt"),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.1, "in"))

Chla1 <- ggplot(mapping = aes(x = Chla, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, col = NA, fill = "royalblue", alpha = 0.5) +
  geom_histogram(data = allSurface_post, col = NA, fill = "chartreuse3", alpha = 0.5) +
  geom_vline(xintercept = thresh_chla2, linetype = "dashed") +
  labs(y = "Proportion", title = "Surface") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

TN1 <- ggplot(mapping = aes(x = TN, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 14.5) +
  geom_histogram(data = allSurface_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 14.5) +
  geom_vline(xintercept = thresh_TN2, linetype = "dashed") +
  xlim(0, 435) +
  ylim(0, 0.41) +
  labs(y = "Proportion", title = "Surface") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

TN2 <- ggplot(mapping = aes(x = TN, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allBottom_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 14.5) +
  geom_histogram(data = allBottom_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 14.5) +
  geom_vline(xintercept = thresh_TN2, linetype = "dashed") +
  xlim(0, 435) +
  ylim(0, 0.41) +
  labs(y = "Proportion", title = "Bottom") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

TP1 <- ggplot(mapping = aes(x = TP, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 1) +
  geom_histogram(data = allSurface_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 1) +
  geom_vline(xintercept = thresh_TP2, linetype = "dashed") +
  xlim(-0.5, 29.5) +
  ylim(0, 0.5) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

TP2 <- ggplot(mapping = aes(x = TP, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allBottom_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 1) +
  geom_histogram(data = allBottom_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 1) +
  geom_vline(xintercept = thresh_TP2, linetype = "dashed") +
  xlim(-0.5, 29.5) +
  ylim(0, 0.5) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

Temp1 <- ggplot(mapping = aes(x = Temp, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, col = NA, fill = "royalblue", alpha = 0.5) +
  geom_histogram(data = allSurface_post, col = NA, fill = "chartreuse3", alpha = 0.5) +
  xlim(0.5, 30.5) +
  ylim(0, 0.205) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

Temp2 <- ggplot(mapping = aes(x = Temp, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allBottom_pre, col = NA, fill = "royalblue", alpha = 0.5) +
  geom_histogram(data = allBottom_post, col = NA, fill = "chartreuse3", alpha = 0.5) +
  xlim(0.5, 30.5) +
  ylim(0, 0.205) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

DO1 <- ggplot(mapping = aes(x = DO, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allSurface_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 0.5) +
  geom_histogram(data = allSurface_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 0.5) +
  geom_vline(xintercept = 3, linetype = "dashed") +
  xlim(-0.25, 14.75) +
  ylim(0, 0.42) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

DO2 <- ggplot(mapping = aes(x = DO, y = after_stat(count / sum(count)))) +
  geom_histogram(data = allBottom_pre, col = NA, fill = "royalblue", alpha = 0.5, binwidth = 0.5) +
  geom_histogram(data = allBottom_post, col = NA, fill = "chartreuse3", alpha = 0.5, binwidth = 0.5) +
  geom_vline(xintercept = 3, linetype = "dashed") +
  xlim(-0.25, 14.75) +
  ylim(0, 0.42) +
  labs(y = "Proportion") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 6))

f2 <- ggarrange(Secchi1, Chla1, TN1, TN2, TP1, TP2, Temp1, Temp2, DO1, DO2, ncol = 2)

ggsave("figures/f2.png", f2, width = 6.5, height = 9, units = "in", dpi = 600)
```

### Pt. 4: DO standard
- Calc "recent" (2016+) & annually in table

### 4a
- All ponds on one graphic; hline @ 3 mg/L
```{r}
allBottom_pre %>%
  group_by(Station.name) %>%
  mutate(DO_lim = ifelse(DO < 3, "< 3", ">= 3")) %>%
  count(DO_lim) %>%
  filter(DO_lim == "< 3")  ## 41

length(unique(allBottom_pre$Station.name))  ## 49

allBottom_post %>%
  group_by(Station.name) %>%
  mutate(DO_lim = ifelse(DO < 3, "< 3", ">= 3")) %>%
  count(DO_lim) %>%
  filter(DO_lim == "< 3")  ## 42

length(unique(allBottom_post$Station.name))  ## 49

f3 <- ggplot(mapping = aes(x = Year, y = DO)) +
  geom_point(data = allBottom) +
  geom_point(data = allBottom_pre, col = "firebrick3") +
  geom_point(data = allBottom_post, col = "firebrick3") +
  geom_hline(yintercept = 3, linetype = "dashed") +
  scale_y_continuous(breaks = c(0, 4, 8, 12)) +
  theme_bw()

ggsave("figures/f3.png", f3, width = 5, height = 3.5, units = "in", dpi = 600)

allBottom_pre %>%
  group_by(Station.name) %>%
  filter(Final.Depth > 9) %>%
  mutate(DO_lim = ifelse(DO < 3, "< 3", ">= 3")) %>%
  count(DO_lim) %>%
  filter(DO_lim == "< 3")  ## 24

length(unique(allBottom_pre$Station.name[allBottom_pre$Final.Depth > 9]))  ## 25

allBottom_post %>%
  group_by(Station.name) %>%
  filter(Final.Depth > 9) %>%
  mutate(DO_lim = ifelse(DO < 3, "< 3", ">= 3")) %>%
  count(DO_lim) %>%
  filter(DO_lim == "< 3")  ## 25

length(unique(allBottom_post$Station.name[allBottom_post$Final.Depth > 9]))  ## 25

f4 <- ggplot(mapping = aes(x = Year, y = DO)) +
  geom_point(data = allBottom[allBottom$Final.Depth > 9, ]) +
  geom_point(data = allBottom_pre[allBottom_pre$Final.Depth > 9, ], col = "firebrick3") +
  geom_point(data = allBottom_post[allBottom_post$Final.Depth > 9, ], col = "firebrick3") +
  geom_hline(yintercept = 3, linetype = "dashed") +
  scale_y_continuous(limits = c(0, 12.25), breaks = c(0, 4, 8, 12)) +
  theme_bw()

ggsave("figures/f4.png", f4, width = 5, height = 3.5, units = "in", dpi = 600)
```

### 4c (Maps w/ trends in all parameters)
```{r}
params <- c("Secchi", "Chla", "TN", "TP", "Temp", "DO", "Alk")

surf_list <- lapply(params, function(param) {
  ggplot() +
    geom_sf(data = mass) +
    geom_point(data = slopes_surf,
               aes(x = Long, y = Lat, size = abs(get(param)), fill = factor(sign(get(param)))),
               shape = 21) +
    geom_point(data = slopes_surf2,
               aes(x = Long, y = Lat, size = abs(get(param)), col = factor(sign(get(param)))),
               shape = 21) +
    scale_size_continuous(range = c(2, 6), name = "Trend\nmagnitude") +
    scale_fill_manual(values = c("royalblue", "firebrick"), 
                      breaks = c(-1, 1),
                      labels = c("negative", "positive"),
                      name = "Trend\ndirection",
                      na.translate = FALSE,
                      guide = "none") +
    scale_color_manual(values = c("royalblue", "black", "firebrick"),
                       breaks = c(-1, 0, 1),
                       labels = c("negative", "zero", "positive"),
                       name = "Trend\ndirection",
                       na.translate = FALSE,
                       guide = "none") +
    xlim(-70.65, -69.95) +
    ylim(41.55, 42.07) +
    labs(title = paste("Surface", param)) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.title = element_blank(),
          #legend.position = "bottom",
          plot.title = element_text(face = "bold"),
          axis.text = element_blank(),
          axis.ticks = element_blank())
})

bott_list <- lapply(params[3:7], function(param) {
  ggplot() +
    geom_sf(data = mass) +
    geom_point(data = slopes_bott,
               aes(x = Long, y = Lat, size = abs(get(param)), fill = factor(sign(get(param)))),
               shape = 21) +
    geom_point(data = slopes_bott2,
               aes(x = Long, y = Lat, size = abs(get(param)), col = factor(sign(get(param)))),
               shape = 21) +
    scale_size_continuous(range = c(2, 6), name = "Trend\nmagnitude") +
    scale_fill_manual(values = c("royalblue", "firebrick"), 
                      breaks = c(-1, 1),
                      labels = c("negative", "positive"),
                      name = "Trend\ndirection",
                      na.translate = FALSE,
                      guide = "none") +
    scale_color_manual(values = c("royalblue", "black", "firebrick"),
                       breaks = c(-1, 0, 1),
                       labels = c("negative", "zero", "positive"),
                       name = "Trend\ndirection",
                       na.translate = FALSE,
                       guide = "none") +
    xlim(-70.65, -69.95) +
    ylim(41.55, 42.07) +
    labs(title = paste("Bottom", param)) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.title = element_blank(),
          #legend.position = "bottom",
          plot.title = element_text(face = "bold"),
          axis.text = element_blank(),
          axis.ticks = element_blank())
})

surf_list[[3]] <- surf_list[[3]] +
  scale_size_continuous(limits = c(0, 5.5), range = c(2, 6), name = "Trend\nmagnitude")

bott_list[[1]] <- bott_list[[1]] +
  scale_size_continuous(limits = c(0, 5.5), range = c(2, 6), name = "Trend\nmagnitude")

surf_list[[4]] <- surf_list[[4]] +
  scale_size_continuous(limits = c(0, 0.4), range = c(2, 6), name = "Trend\nmagnitude")

bott_list[[2]] <- bott_list[[2]] +
  scale_size_continuous(limits = c(0, 0.4), range = c(2, 6), name = "Trend\nmagnitude")

surf_list[[5]] <- surf_list[[5]] +
  scale_size_continuous(limits = c(0, 0.8), range = c(2, 6), name = "Trend\nmagnitude")

bott_list[[3]] <- bott_list[[3]] +
  scale_size_continuous(limits = c(0, 0.8), range = c(2, 6), name = "Trend\nmagnitude")

surf_list[[6]] <- surf_list[[6]] +
  scale_size_continuous(limits = c(0, 0.65), range = c(2, 6), name = "Trend\nmagnitude")

bott_list[[4]] <- bott_list[[4]] +
  scale_size_continuous(limits = c(0, 0.65), range = c(2, 6), name = "Trend\nmagnitude")

surf_list[[7]] <- surf_list[[7]] +
  scale_size_continuous(limits = c(0, 4.5), range = c(2, 6), name = "Trend\nmagnitude")

bott_list[[5]] <- bott_list[[5]] +
  scale_size_continuous(limits = c(0, 4.5), range = c(2, 6), name = "Trend\nmagnitude")

f5 <- ggarrange(surf_list[[1]], surf_list[[2]],
                surf_list[[3]], bott_list[[1]],
                surf_list[[4]], bott_list[[2]], ncol = 2)

ggsave("figures/f5.png", f5, width = 6.5, height = 7, units = "in", dpi = 600)

f6 <- ggarrange(surf_list[[5]], bott_list[[3]],
          surf_list[[6]], bott_list[[4]],
          surf_list[[7]], bott_list[[5]], ncol = 2)

ggsave("figures/f6.png", f6, width = 6.5, height = 7, units = "in", dpi = 600)
```
